---
title: "Homework 1 Notebook"
author: "Name"
date: "08-30-2019"
output: html_notebook
---


1) Read the "What is Data Science?" article posted on D2L and respond to the following prompts.

a) Based on your reading of the posted article, compare and contrast coputer science, data science, and real science. 

b) What interesting questions can you ask and answer with the baseball data from section 1.2.1 of the reading? 

c) What interesting questions can you ask and answer with the movie data from section 1.2.2 of the reading? 

d) Describe what is meant by a taxonomy of the properties of data discussed in section 1.3 of the reading. 

e) Define classification and provide an example. 

f) Define regression and provide an example. 

g) What is kaggle? 

2) Complete the swirl lesson 1: Basic Building Blocks from the R Programming swirl course and respond to the following prompts. 

a) What is the assignment operator in R? 

b) What is a data structure and what is a numeric vector in R? 

c) True or False: In R a single number is considered a vector of length one. 

d) How do you create a vector in R? 

e) How do you access R's built-in help files? 

f) In R is it possible to combine vectors to create a new vector? If so, how? 

g) In the following R code block, create a vector that contains the values 2, 7, 82.3 and assign it to a variable called my_vect. 

```{r}
# type R code here
```


h) After running your code for part g), run the code below and explain the output. 

```{r}
my_vect^2
```


i) What happens in R if you add two vectors of different lengths? Run the following code and explain the output.

```{r}
x <- c(1,2,3,5)
y <- c(-2,3)
x + y
```

Now explain the output from this code
```{r}
x <- c(1,2,3,4,5)
y <- c(-1,2)
x + y
```


